Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
Comment out acknowledgements.
More revisions to architecture.

% out of order, blah blah.
% "concatenates successive bodies"
% handle it by strict serialization, has performance issues, see ...

HTTP is fundamentally a pull-based protocol.
There is no way for the server to send data to the client without
the client first making a request.
The same applies to meek: when \meekserver\ has data to send back to
a client with a particular session ID, it cannot do so until it
receives a request from that client.
For this reason, \meekclient\ polls the server,
sending an empty request if necessary, every so often.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
Alternative techniques for push-like behavior,
such as HTTP long polling,
don't work well with App Engine,
because App Engine requires requests to finish within 60 seconds.
% Psiphon did it.

@@

% Psiphon idea: use long-polling for downstream data.
% Works with CDNs, not with App Engine.

\section{Future work}

@@

\section*{Acknowledgments}

We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
Special thanks go to the members of the tor-qa and tor-dev mailing lists
who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Rod Hynes and Michael Hull of Psiphon.
% Ox from Lantern.
% Johanna Amann for getting the fraction of SNI from ICSI notary:
%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
% Arlo Breault (flashproxy-reg-appspot)

>>>>

The underlying TCP stream is broken into chunks so that
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
meek takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
receive the response to the first request.
The underlying stream is simply the concatenation
of chunks in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
The performance drawbacks are not inherent to the design:
it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
Section~\ref{sec:futurework} describes more efficient encodings
that enable multiple requests in parallel.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique is to use
long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
See Section~\ref{sec:otherdeployment} for more details
on when each technique may be used.

@@

% Psiphon idea: use long-polling for downstream data.
% Works with CDNs, not with App Engine.
% Alternative techniques for push-like behavior,
% such as HTTP long polling,
% don't work well with App Engine,
% because App Engine requires requests to finish within 60 seconds.

\section{Future work}
\label{sec:futurework}

@@

% \section*{Acknowledgments}

% We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
% Special thanks go to the members of the tor-qa and tor-dev mailing lists
% who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Rod Hynes and Michael Hull of Psiphon.
% Ox from Lantern.
% Johanna Amann for getting the fraction of SNI from ICSI notary:
%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
% Arlo Breault (flashproxy-reg-appspot)
